---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

options(whirl.verbosity_level = "minimal")
```

# whirl

<!-- badges: start -->

[![R-CMD-check](https://github.com/NN-OpenSource/whirl/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/NN-OpenSource/whirl/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

##  Overview

The whirl package provide functionalities for executing scripts in batch and simultaneously getting a log from the individual executions. 
A log from script execution is in many pharmaceutical companies a GxP requirement, and the whirl package honors this requirement by generating a log that, among other things, contains information about:

* Status (did the script run with any error or warnings)
* The actual code itself
* Date and time of execution
* The environment the script was executed under (session info)
* Information about packages versions that was utilized
* Environmental variables  

And all this is wrapped into a nicely formatted html document that is easy to navigate. 

## Usage

The main function in the whirl package is `run()` which takes an `input` argument
that defines the scripts to be executed.

The simplest way is to provide the path to a single script:

```{r ex-script}
library(whirl)
script <- system.file("examples/simple/success.R", package = "whirl")
run(script)
```
It is also possible to run several scripts simultaneously:

```{r ex-scripts}
scripts <- system.file("examples/simple", c("success.R", "warning.R"), package = "whirl")
result <- run(scripts, n_workers = 2)
```

Here we are specifying that `run()` can use up to two simultaneous workers to execute the scripts,
meaning that they will be executed in parallel.

When using `run()` the following files are created:

1. Creates a log in the same directory as the script with the names `{script_name}_log.html`. See [example_log.html](articles/example_log.html) for an example of a simple log.
1. Creates a summary log with the overall status of each script. Default path is `summary.html`. See [summary.html](articles/summary.html) for an example of a summary of the same log as above.

Apart from this the function also returns a `tibble` with the status of the script execution similar to the content of the summary above:

```{r ex-return}
print(result)
```

## Config files

`run()` also supports running scripts in several sequential steps. 
This setup is very useful when your projects have several steps that depends on each others output, and thereby need to be executed in a specific order.
The best way to implement this in your project is use a configuration file for whirl. 
The configuration file is a `yaml` file that specifies each steps:

```{r ex-config}
config <- system.file("examples/simple/_whirl.yaml", package = "whirl") 
cat(readLines(config), sep = "\n")
```

Here we are specifying that in the first step we run `succes.R`. And then when this step has been completed we continue to running 
the scripts in the second steps. 

```{r ex-run-config}
result <- run(config, n_workers = 2)
```

```{r, ex-return-config}
print(result)
```


## Customize run()

For more information about how to customize the the execution and the logging for your needs see the following:

* `run()`: For further information on how to call it.
* `vignette("whirl")`: For a more in depth explanation, and more advanced usage.
* `vignette("example")`: With a simple example, including the created log.
* `options()`: On how to change the default behavior of whirl.
