---
title: "Execute Scripts"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Execute Scripts}
  %\VignetteEngine{knitr::rmarkdown_notangle}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

# Introduction

The whirl package provides functionalities for executing scripts in batch while simultaneously getting logs from the individual executions. In the following sections, we will go through how to use the package.

# Ways to call the `run()` function

## Single and multiple files, and wild cards

The `input` argument in the `run()` function can in the most simple case point to a single file for which an execution and log-generation is required. 

```{r}
library(whirl)
run(input = "path/to/script.R")
```

The `input` argument can also point to multiple files in a directory using wildcard (or globbing) patterns. 
In this case, all scripts in the directory will be executed in parallel and a log will be generated for each script.
The number of workers can be specified through the `n_workers` argument (default is set to one).
A summary log file will also be provided as a fast way to get an overview of the execution. 
The location of the summary file can be controlled with the `summary_file` argument.

```{r}
# Execution of all R files in a specific directory
run(
  input = "path/to/directory/*.R",
  n_workers = 4,
  summary_file = "path/to/summary"
)

# Execution of all R files starting with "mk200" in a specific directory
run(
  input = "path/to/directory/mk200*.R",
  n_workers = 8,
  summary_file = "path/to/summary"
)
```

More information on how the wildcards are interpreted see `Sys.glob()`.

It is also possible to provide a character vector of several paths (either single files or glob expression) that should be executed. Note that whenever the `input` argument in is supplied with a character vector (e.g. `c("path/to/script1.R", "path/to/script2.R")`) it assumes that these can be executed independently and in parallel. If the elements needs to be executed sequentially this can be achieved by using a `list()` instead (see below).

## Using `list()` as input

If the scripts have to be executed in a specific order, the `input` argument can be supplied as a list. The scripts will then be executed in the order they are listed in the list, with scripts listed in the same element being executed in parallel (if `n_workers` > 1). 

```{r}
# In the below example, script1.R and script2.R will be executed in parallel
run(
  input = c(
    "path/to/script1.R",
    "path/to/script2.R"
  ),
  n_workers = 2
)

# In the below example, script1.R and script2.R will be executed in parallel,
# and all R files in the directory will subsequently be executed in parallel
run(
  input = list(
    c("path/to/script1.R", "path/to/script2.R"),
    "path/to/directory/*.R"
  ),
  n_workers = 2
)

# In the below example, script1.R and script2.R will be executed in parallel,
# and subsequently script3.R and script4.R will be executed in parallel
run(
  input = list(
    c("path/to/script1.R", "path/to/script2.R"),
    c("path/to/script3.R", "path/to/script4.R")
  ),
  n_workers = 2
)
```

The list can also be supplied with names list elements. 
This can be useful during execution as some of these 'name' will be printed to the console.

E.g.
```{r}
run(
  input = list(
    list(
      name = "Step 1",
      paths = c("path/to/script1.R", "path/to/script2.R")
    ),
    list(
      name = "Step 2",
      paths = c("path/to/script3.R", "path/to/script4.R")
    )
  ),
  n_workers = 2
)
```

## Using a configuration file as input

The execution order can also be pre-specified in a configuration file (config file for short). 
The config file could have the following structure. 

```yaml
steps:
  - name: "Step 1"    
    paths:    
      - "path/to/script1.R"
      - "path/to/script2.R"
  - name: "Step 2"  
    paths:    
      - "path/to/script3.R"
      - "path/to/script4.R"
```

In this case, the `input` argument in the `run()` function should point to the config file. 
Assuming the config file is called `config.yaml`, the execution can be initiated as follows:

```{r}
run(input = "path/to/config.yaml", n_workers = 4)
```

Each steps in the config file will be executed independently while scrips within each step will be executed in parallel using the number of workers specified with the `n_workers` argument.

# Adjusting the log directory
## How to use the `log_dir` argument to specify where to store the logs
When executing `run()` the default is to store logs in the directory where the individual scripts are located. For example, if we apply `run()` to a a vector of scripts with the following paths `c(path/to/dir1/script1.R, path/to/dir2/script2.R)`, the log of script1.R and script2.R will be stored in **path/to/dir1** and **path/to/dir2**, respectively.

If the logs should be stored in a different directory, the `log_dir` argument can be used. 
This argument can be supplied with a character string or a function. Note that in either case the directory that `log_dir` points to must exist before the execution is initiated.  

If the `log_dir` is supplied with a character pointing to a specific path the call could look like:

```{r}
run(input = "path/to/script.R", log_dir = "path/to/logs")
```

In this example the log of script.R will be stored in **path/to/logs**.  
Note that if multiple scripts are executed and `log_dir` is a character to a path, then every log will be redirected to the same directory - in this case **path/to/logs**.


If a more dynamic approach is needed the `log_dir` argument can also be supplied with a function that will be applied to the individual path of every script.  
For example, if multiple script are executed and the logs needs to be stored in a sub-folder within the script directories this could be achieved by:

```{r}
run(
  input = c("path/to/dir1/script1.R", "path/to/dir2/script2.R"),
  log_dir = function(x) {
    paste0(dirname(x), "/logs")
  }
)
```

In this example the log of script1.R will be stored in **path/to/dir1/logs** and the log of script2.R will be stored in **path/to/dir2/logs**.

Note that **x** refer to the path of the script that is being executed. 
