---
title: "Log example"
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

system.file("examples/prg1.R", package = "whirl") |> 
  file.copy(to = "example.R")
```

In this example we are going to execute the following script and create a log of it's execution:

```{r, echo = FALSE}
readLines("example.R") |> 
  cli::cli_code()
```

We are going to use the `run()` function to execute the script, and since this vignette
is created on Linux we can use the `whirl.track_files` option to automatically track the used files: 

```{r whirl-setup}
library(whirl)

options(whirl.track_files = TRUE)
options(whirl.verbosity_level = "minimal")
```

The `verbosity_level` is set to `minimal` for nicer printing in ths vignette.
Now we are ready to execute the script:

```{r run}
result <- run("example.R")

print(result)
```

The script is now executed and you can access the logs below:

```{r copy, include=FALSE}
file.copy(from = "summary.html", to = "../docs/articles")
file.copy(from = "example_log.html", to = "../docs/articles")
```

* [View summary log](summary.html)
* [View log for example.R](example_log.html)
* [The saved plot1.png](plot1.png)
