---
title: "Log example"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

# Use a temporary directory as working directory with the example program

wd <- getwd()
tmp <- withr::local_tempdir()

system.file("examples/prg1.R", package = "whirl") |>
  file.copy(to = file.path(tmp, "example.R"))

knitr::opts_knit$set(root.dir = tmp)
```

In this example we are going to execute the following script and create a log of it's execution:

`example.R:`
```{r, file = "example.R", eval = FALSE}
```

We are going to use the `run()` function to execute the script, and since this vignette
is created on Linux we can use the `whirl.track_files` option to automatically track the used files: 

```{r whirl-setup}
library(whirl)

options(whirl.track_files = TRUE)
options(whirl.verbosity_level = "minimal")
```

The `verbosity_level` is set to `minimal` for nicer printing in this vignette.
Now we are ready to execute the script:

```{r run}
result <- run("example.R")

print(result)
```

The script is now executed and you can access the logs below:

```{r copy, include=FALSE}
# Also check if all outputs were created as expected
withr::with_dir(tmp, {
  articles_folder <- file.path(wd, "../../docs/articles")

  articles_folder |>
    dir.exists() |>
    stopifnot()

  c("summary.html", "example_log.html", "plot1.png") |>
    lapply(file.copy, to = articles_folder, overwrite = TRUE) |>
    unlist() |>
    all() |>
    stopifnot()
})
```

* [View summary log](summary.html)
* [View log for example.R](example_log.html)
* [The saved plot1.png](plot1.png)
